\documentclass{homeworg}

\title{Problem Set 1}
\author{Karley Nadolski}

\begin{document}

\maketitle

\section{Introduction}
It wasn't until I really understood that economics is the study of relationships that I started to love it. I was fascinated by economic theories that explained things that I always assumed were natural. Over the last four years at OU, I've taken classes to expand my understanding of economics and how theoretical concepts can be applied to the study of real-life conditions. Much of my interest in data science comes from wanting to have a better understanding of how to study economics, and economic relationships, in 2021. 

I am a fast learner, but the hardest part of my econ classes has been getting a good grasp on the math needed for advanced economic analysis. Over the last few semesters, I have devoted more time to learning about the foundations of statistics (Bayesian and classical) and the calculus underpinning different economic theories. As I've been able to invest in those skills, I realized that a better understanding of the foundational math would only strengthen my grasp on the economic relationships that I was so interested in. I approach data science in much the same way. Studying economics has changed the way that I think and problem solve, I hope learning more about data science will help shape that. 

Right now, I am really unsure about what direction to take my research for this class. Usually the topics that most interest me have to do with policy and public response. If I can find a research topic that integrates economics and constitutional law, I would be pretty happy about that. 

After graduation, I am planning on working for a year or two. Ideally, I would be able to find a job that asks me to use what I've learned in economic reasoning and data practices. I've already applied to a few positions for which this class will be especially helpful in getting me ready. After those years, though, I plan on going to law school. Studying economics has given me tools for making decisions and problem solving, I ultimately hope to apply these skills to studying/practicing law. 

\section{Equation}

\[ a^2 + b^2 = c^2\]


\end{document}
